\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-03-25 doc/sw-system.tex
Implemented \StageOne and \StageTwo macros, closes #109

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Space Warps System Paper
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We describe \sw, a novel gravitaional lens discovery service that
yields samples of high purity and completeness through crowd-sourced
visual inspection.
Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``stage 1'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
stage 1 candidates; these were then refined to yield a sample of 1400
candidates rankable by their stage 2 probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \sw system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

@@

In this paper, we describe the \sw web application, an
online system that was conceived to address the visual inspection problem in
gravitational lens detection for future large surveys via crowd-sourcing, and
implemented as a Zooniverse project.
In a companion paper (More et al, in preparation, herafter \papertwo) we will
present the new gravitational lenses discovered in our first, experimental,
lens search, and begin to investigate the differences between lens detections
made in \sw and those made with automated techniques. Here though, we simply
try to answer the following questions:

@@

Our basic method in this paper is to analyze the performance of the \sw system
on the ``training set'' of simulated lenses and known non-lenses. This allows
us to estimate completeness and purity with respect to gravitational lenses
that have the same properties of the training set. In \papertwo,
we carry out a complementary analysis using a sample of
``known'' (reported in the literature) lenses.

@@

\subsubsection{Stage 1: Initial Classification}

The goal of a stage 1 classification is to achieve a high rejection rate,
while maintaining high completeness.  In this mode, therefore, the pre-loading
of images was used to make the sliding in of new subjects happen quickly, to
provide a sense of urgency: initial classification must be done fairly
quickly for the search to be completed within a reasonable time period.  We
expect some trade-off between speed and accuracy, which we return to in the
results section below. Completion of the search requires subjects to be
``retired'' over time, as a result of their being classified. We did this by
analyzing the classifications on a daily basis, as described in
\Sref{sec:swap} below. As subjects were retired, new ones were ingested into
the web app for classification. This means that the discovery of lens
candidates in stage 1 is truly a community effort: to detect a lens candidate,
many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.

The stage 1 training set was chosen to be quite clear cut, in order to err on
the side of inclusivity, and so ensure high completeness. For the training duds
we selected several hundred images at random, and three of us (AM, with AV and
PM) inspected them and discarded anything that could be considered a lens
candidate: this meant that objects that looks similar to lenses, such as galaxy
mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
specifically excluded from the training set, and so we expect some of those
types of object to appear in the stage 1 candidate list. The training sims for
stage 1 were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like. We return to this balance below.

\subsubsection{Stage 2: Refinement}

The design of the stage 1 classification task, and its training set, should lead
to sample of lens candidates that has high completeness but may have low purity.
To refine this sample to higher purity, we need to reject more non-lenses, which
means providing the volunteers with a more realistic and challenging training
set as they re-classify it. The more demanding stage 2 training set was
generated as follows. The stage 2 duds were selected from the image pool by at
least one of three of us  (AV, AM and PM) as being a potential false positive,
while the stage 2 sims were chosen to be a subset of stage 1 sims, none of which
were deemed ``obvious'' by the same expert classifiers.
\Fref{fig:training:gallery} shows some example images from the resulting CFHTLS
stage 2 training set.

@@

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the stage 2 training set. Insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the stage 2 training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses; the insets merely indicate regions where $\sim10\%$ of the
volunteers clicked.} \label{fig:training-gallery:duds}
\end{figure*}

@@

We refer the reader to \papertwo for the details of the particular set of
imaging survey data used in this first \sw project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \sw system.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW stage 1 subject trajectories. Subjects drift downwards in
the top panel as they are classified, while being nudged left and right by the
Agents as they interpret the volunteers input. The dotted vertical lines show
(left to right) the retirement threshold, prior probability, and the detection
threshold.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

During stage 1 classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them. The
progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
Subjects appear on this plot at the tip of the arrow, at zero classifications
and prior probability; they then drift downwards as they are classified by the
crowd, with each Agent applying the appropriate kick in probability based on
what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
with high probability, while duds (red) pile up at low probability; test
subjects (black) mostly drift to low probability, but some go the other way.
The latter will help make up the candidate sample. As this plot shows, around
10 classifications are required for a subject to reach the retirement
threshold.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for stage 2. The sample of
subjects classified during stage 2 was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at stage 1. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at stage 2 was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \sw crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the
properties of the agents described in the text. The stage 1 agents are shown
in blue, the stage 2 agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In stage 1, the mean effort per agent was 263; in the shorter stage
2 it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In stage 1, the mean experience per agent was 29;
in stage 2 (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain,
$\skill$
should  the next subject classified have lens probability 0.5
(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In stage 1, the mean skill per agent
was 0.04 bits; in  stage 2 it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In stage 1, the mean contribution per agent was 34.9 bits; in
stage 2 it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

@@

The distributions for the stage 2 agents (orange) are qualitatively similar to
those for the stage 1 agents (blue). Differences are: 1) the maximum effort
possible at stage 2 is smaller, because fewer subjects were available to be
classifed, but 2) the mean effort expended at stage 2 was higher (perhaps
because the subjects were higher probability, and more compelling); 3) the
information generated per agent was higher at stage 2, because the subjects
had higher probability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulative distributions of the contributions made by the
agents: for example, 90\% of the stage 2 contributions were made by the
highest contributing  7\% of the crowd. The stage 1 agents are shown in blue,
the stage 2 agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
stage 1,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At stage 2, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at stage 1, and 77\% at stage 2. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
\caption{Broad cumulative distributions of agent skill:
the most skilled 20\% of the crowd only possess 79\% of the skill at stage 1.
The stage 1 agents
are shown in blue, the stage 2 agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

How fast does the \sw crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both Stage 1 and Stage
2 in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. Stage 1 (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of Stage 1, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) Stage 2 (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

@@

The similarities between Stage 1 and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy). For example, the completion time for a \SW project could be approximated as
\begin{equation}
    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
                               \left(\frac{N_s}{10^4}\right),
\end{equation}
where $N_s$ is the number of subjects to be classified, and $N_p$ is the number of volunteers in the crowd.

@@

The lensed quasar part of the training set yielded the highest
completeness, suggesting that these were the easiest sims to spot. The lensed
galaxies were recovered at understandably lowest completeness, although the
wider image separation  lensing clusters were not very different. At stage 2,
where no retirement was carried out, it was possible to reach 100\% purity:
indeed, the knee of the curve is at just under 90\% completeness. However, the
purity decreases rapidly if higher completeness than this is sought.
Interestingly, the lensing clusters can be seen to pose problems for the
system, with its curve turning over at just 60\% completeness.

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the stage 2 false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw system, and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \sw system. While the final stage 2 analysis was done offline,
these trajectory plots still serve to illustrate the approximate
classification histories of the subjects.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% Space Warps Paper I: System
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We describe \sw, a novel gravitaional lens discovery service that
yields samples of high purity and completeness through crowd-sourced
visual inspection.
Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``\StageOne'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 70 by 70 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
\StageOne candidates; these were then refined to yield a sample of 1400
candidates rankable by their \StageTwo probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \sw system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

@@

In this paper, we describe the \sw web application, an
online system that was conceived to address the visual inspection problem in
gravitational lens detection for future large surveys via crowd-sourcing, and
implemented as a Zooniverse project.
In a companion paper (More et al, in preparation, herafter \PaperTwo) we will
present the new gravitational lenses discovered in our first, experimental,
lens search, and begin to investigate the differences between lens detections
made in \sw and those made with automated techniques. Here though, we simply
try to answer the following questions:

@@

Our basic method in this paper is to analyze the performance of the \sw system
on the ``training set'' of simulated lenses and known non-lenses. This allows
us to estimate completeness and purity with respect to gravitational lenses
that have the same properties of the training set. In \PaperTwo,
we carry out a complementary analysis using a sample of
``known'' (reported in the literature) lenses.

@@

\subsubsection{\StageOne: Initial Classification}

The goal of a \StageOne classification is to achieve a high rejection rate,
while maintaining high completeness.  In this mode, therefore, the pre-loading
of images was used to make the sliding in of new subjects happen quickly, to
provide a sense of urgency: initial classification must be done fairly
quickly for the search to be completed within a reasonable time period.  We
expect some trade-off between speed and accuracy, which we return to in the
results section below. Completion of the search requires subjects to be
``retired'' over time, as a result of their being classified. We did this by
analyzing the classifications on a daily basis, as described in
\Sref{sec:swap} below. As subjects were retired, new ones were ingested into
the web app for classification. This means that the discovery of lens
candidates in \StageOne is truly a community effort: to detect a lens candidate,
many non-lenses must first be rejected, and several classifications by different inspectors are needed in either case.

The \StageOne training set was chosen to be quite clear cut, in order to err on
the side of inclusivity, and so ensure high completeness. For the training duds
we selected several hundred images at random, and three of us (AM, with AV and
PM) inspected them and discarded anything that could be considered a lens
candidate: this meant that objects that looks similar to lenses, such as galaxy
mergers, tidal tails and spiral arms, pairs of blue stars and so on, were
specifically excluded from the training set, and so we expect some of those
types of object to appear in the \StageOne candidate list. The training sims for
\StageOne were also selected to be relatively straightforward to spot, as we sought a balance between sensitivity to faint or difficult lenses, and the need to educate the volunteers in what gravitational lenses look like. We return to this balance below.

\subsubsection{\StageTwo: Refinement}

The design of the \StageOne classification task, and its training set, should lead
to sample of lens candidates that has high completeness but may have low purity.
To refine this sample to higher purity, we need to reject more non-lenses, which
means providing the volunteers with a more realistic and challenging training
set as they re-classify it. The more demanding \StageTwo training set was
generated as follows. The \StageTwo duds were selected from the image pool by at
least one of three of us  (AV, AM and PM) as being a potential false positive,
while the \StageTwo sims were chosen to be a subset of \StageOne sims, none of which
were deemed ``obvious'' by the same expert classifiers.
\Fref{fig:training:gallery} shows some example images from the resulting CFHTLS
\StageTwo training set.

@@

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/4.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/5.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/6.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/7.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``sims'' from the \StageTwo training set. Insets indicate the
location of the simulated lens in each of these training images. Users needed to
click on these specific features in order to make a correct classification.}
\label{fig:training-gallery:sims}
\end{figure*}

\begin{figure*}%[!ht]
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/0.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/1.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/2.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\begin{minipage}[b]{0.24\linewidth}
\centering\epsfig{file=sw-system-figs/gallery/3.png,width=\linewidth,angle=0,clip=}
\end{minipage} \hfill
\caption{Typical \SW ``duds'' from the \StageTwo training set. All of these
subjects were correctly classified by the community as not likely to contain
gravitational lenses; the insets merely indicate regions where $\sim10\%$ of the
volunteers clicked.} \label{fig:training-gallery:duds}
\end{figure*}

@@

We refer the reader to \PaperTwo for the details of the particular set of
imaging survey data used in this first \sw project. Here, we summarize very
briefly the choices that were made, in order to provide the context for our
general description and illustrations of the \sw system.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/CFHTLS_2013-10-29_10:16:35_trajectories.png}
\caption{Typical \SW \StageOne subject trajectories. Subjects drift downwards in
the top panel as they are classified, while being nudged left and right by the
Agents as they interpret the volunteers input. The dotted vertical lines show
(left to right) the retirement threshold, prior probability, and the detection
threshold.}
\label{fig:swap:subject-trajectories}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

During \StageOne classification of the CFHTLS images, we assigned a prior
probability for each image to contain a lens of $2\times10^{-4}$, based on a
rough estimate of the number of expected lenses in the survey. We then
assigned two values of the images' posterior probability, $\pr(\LENS|C,T)$, to
define ``detection'' and ``rejection'' thresholds. These were set to be 0.95
and (approximately symmetrically in the logarithm of probability), $10^{-7}$.
Subjects that attained probability of less than the rejection threshold were
scheduled for retirement and subsequently ignored by the analysis code.
Subjects crossing the detection threshold were not retired from the website,
but instead left in the system so that more volunteers could see them. The
progress of the subjects is illustrated in \Fref{fig:swap:subject-trajectories}.
Subjects appear on this plot at the tip of the arrow, at zero classifications
and prior probability; they then drift downwards as they are classified by the
crowd, with each Agent applying the appropriate kick in probability based on
what it hears its volunteer say. Encouragingly, sims (blue) tend to end up
with high probability, while duds (red) pile up at low probability; test
subjects (black) mostly drift to low probability, but some go the other way.
The latter will help make up the candidate sample. As this plot shows, around
10 classifications are required for a subject to reach the retirement
threshold.

@@

When all the subjects had either been retired, or classified around 10 times
or more, the web app was paused and reconfigured for \StageTwo. The sample of
subjects classified during \StageTwo was selected to be all those that passed
the detection threshold ($\pr(\LENS|C,T) > 0.95$) at \StageOne. These were
classified for one week, with no retirement but a maximum classification
number of 50 each. The number of subjects at \StageTwo was small enough that we
did not need to retire any: instead, we simply collected classifications for a
fixed period of time (about 4 weeks). Without the time pressure motivating the
online analysis, we implemented an ``offline'' version of the analysis that
performs a joint inference of all Agent confusion matrix elements and subject
probabilities simultaneously, for comparison. We describe how this differs
from the online analysis in the appendix.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/all_skill_contribution_experience_education.png}
\caption{Key properties and contributions of the \sw crowd. Plotted are the
1-D and 2-D marginalized distributions for the logarithms of the
properties of the agents described in the text. The \StageOne agents are shown
in blue, the \StageTwo agents in orange.}
\label{fig:crowd:cornerplot}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We define the following properties of the crowd, as characterised by their
agents, and plot the distributions of their logarithms in
\Fref{fig:crowd:cornerplot}.
%
\begin{description}
%
\item{\noindent\bf ``Effort:''} The number of test images, $\effort$, classified by a
volunteer. In \StageOne, the mean effort per agent was 263; in the shorter \StageTwo it was 81.
%
\item{\noindent\bf ``Experience:''} The number of training images, $\experience$,
classified by a volunteer. In \StageOne, the mean experience per agent was 29;
in \StageTwo (where the training image fequency was set higher) it was 34.
%
\item{\noindent\bf ``Skill:''} The expectation value of the information gain,
$\skill$
should  the next subject classified have lens probability 0.5
(\Aref{appendix:swap}),  in bits. Random classifiers have $\skill = 0.0$,
perfect classifiers have $\skill = 1.0$. All agents start with $\skill = 0.0$;
this increases as training subjects are classified, and the agent's estimates
of its confusion matrix elements improve. In \StageOne, the mean skill per agent
was 0.04 bits; in  \StageTwo it was 0.05.
%
\item{\noindent\bf ``Contribution:''} The integrated skill over a volunteer's test
subject classification history, and represents the total  contribution to the
project that volunteer (see the appendix for more discussion of this
quantity). In \StageOne, the mean contribution per agent was 34.9 bits; in
\StageTwo it was 33.5.
%
\item{\noindent\bf ``Information:''} The total information $\information$ generated by
the  agent during the volunteer's classification activity. This quantity
depends on the value of each subject's lens probability when that subject was
presented to the volunteer (\Aref{appendix:swap}), and so there is an element
of luck involved with this quantity: if you never see a high probability
subject, it's hard to generate a large amount of information. You make your
own luck by classifying more subjects.
%
\end{description}

@@

The distributions for the \StageTwo agents (orange) are qualitatively similar to
those for the \StageOne agents (blue). Differences are: 1) the maximum effort
possible at \StageTwo is smaller, because fewer subjects were available to be
classifed, but 2) the mean effort expended at \StageTwo was higher (perhaps
because the subjects were higher probability, and more compelling); 3) the
information generated per agent was higher at \StageTwo, because the subjects
had higher probability.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_contrib_cumul.png}
\caption{Narrow cumulative distributions of the contributions made by the
agents: for example, 90\% of the \StageTwo contributions were made by the
highest contributing  7\% of the crowd. The \StageOne agents are shown in blue,
the \StageTwo agents in orange. ``Experienced volunteers'' classified 10 or more
training subjects.}
\label{fig:crowd:cumulplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Fref{fig:crowd:cornerplot} shows the \sw crowd to have quite broad
distributions of logarithmic effort, skill, and contribution. To better
quantify the contributions made by the volunteers, we show their cumulative
distribution on a linear scale in \Fref{fig:crowd:cumulplot}. This plot shows
clearly the importance of the hardest-working, most active volunteers: at
\StageOne,  1.0\% of the volunteers -- 375 people -- made 90\% of the
contribution.  At \StageTwo, where it was not possible to make as
many classifications before running out of subjects, 7.2\% of the volunteers
-- 141 people -- made 90\% of the contribution.

However, it is not the case that only these small groups were capable of
making this large contribution.
% : 9118 volunteers were ``experienced'' in that
% they had all classified at least 10 training images; the 375 highest
% contributing volunteers make up just 4\% of this experienced volunteer pool.
The cumulative distribution of agent skill is shown in
\Fref{fig:crowd:cumulskillplot}: these distributions are significantly broader
than the corresponding distributions of agent contribution in
\Fref{fig:crowd:cumulplot}. The most skilled 20\% of agents possess only  79\%
of the skill at \StageOne, and 77\% at \StageTwo. The inexperienced volunteers
also possess a significant fraction of the skill: the most skillful 20\% of
experienced volunteers (1824 people)  possess just 43\% of the total skill.
The level of contribution made at \sw by experienced volunteers is largely a
matter of choice (or perhaps, availability of time!).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/crowd_skill_cumul.png}
\caption{Broad cumulative distributions of agent skill:
the most skilled 20\% of the crowd only possess 79\% of the skill at \StageOne.
The \StageOne agents
are shown in blue, the \StageTwo agents in orange. ``Experienced volunteers''
classified 10 or more training subjects.}
\label{fig:crowd:cumulskillplot}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

How fast does the \sw crowd classify subjects? Each agent records the timestamp
of each classification its volunteer makes; by measuring the time lags between
successive classifications we can make estimates of the crowd's classification
and contribution speed. We plot these two quantities for both \StageOne and \StageTwo in \Fref{fig:results:speed}, normalizing the speed and time axes to the
respective totals. The fractional classification rates in each stage of the survey fall off in approximately the same way, despite the factor of nearly 20 difference in crowd size. \StageOne (consisting of $\sim430,000$ subjects) was completed in around 5000 hours (by some 37,000 participants), with classification rates in the first few days averaging at $\sim10^4$ per hour, stimulated by various forms of advertising (press releases, and emails to registered Zooniverse users). The asymptotic classification rate was $\sim10^3$ per hour. The average skill was found to be approximately constant over the lifetime of \StageOne, leading to a contribution rate that tracks closely the classification rate. (A 10\% increase in average skill was seen over the first 40 days, and a decrease of the same amount in the last 40 days -- not enough to cause a significant difference between classification and contribution rate behavior, but perhaps reflecting a learning period at the start and a decrease in participation late on.) \StageTwo (3700 subjects) was completed in around 600 hours by around 2000 participants, with classification rates starting at $~\sim2000$ per hour and decaying to $\sim100$ per hour.

@@

The similarities between \StageOne and 2, suggest that these numbers could be scaled to estimate the speed of future \SW projects (or at least those following a similar blind search strategy). For example, the completion time for a \SW project could be approximated as
\begin{equation}
    \tau \approx 18\,{\rm days} \left(\frac{10^4}{N_p}\right)
                               \left(\frac{N_s}{10^4}\right),
\end{equation}
where $N_s$ is the number of subjects to be classified, and $N_p$ is the number of volunteers in the crowd.

@@

The lensed quasar part of the training set yielded the highest
completeness, suggesting that these were the easiest sims to spot. The lensed
galaxies were recovered at understandably lowest completeness, although the
wider image separation  lensing clusters were not very different. At \StageTwo,
where no retirement was carried out, it was possible to reach 100\% purity:
indeed, the knee of the curve is at just under 90\% completeness. However, the
purity decreases rapidly if higher completeness than this is sought.
Interestingly, the lensing clusters can be seen to pose problems for the
system, with its curve turning over at just 60\% completeness.

@@

We investigated the source of the incompleteness and impurity visible in
\Fref{fig:results:sample:CP}, by examining the \StageTwo false negatives and
false positives, and their behaviour as they are classified using the online
analysis trajectory plots introduced in \Sref{sec:swap}
(\Fref{fig:swap:subject-trajectories}).
\Fref{fig:discuss:performance:trajectories} shows 2 example simulated lenses
that were missed ($\pr(\LENS|C,T) < 10^{-5}$) by the \sw system, and 2 example
non-lenses that were incorrectly flagged as candidates ($\pr(\LENS|C,T) >
0.95$) by the \sw system. While the final \StageTwo analysis was done offline,
these trajectory plots still serve to illustrate the approximate
classification histories of the subjects.
